\huge Tor's Usability for Censorship Circumvention

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
fix another sentence.

\subsubsection{Time to Success} 
Time to success is defined as the time until the first successful connection to Tor. Non-finishing participants are assigned the maximum experiment time of 40:08.  {\color {red} Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).} The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). 
Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.

>>>>

\subsubsection{Time to Success} 
Time to success is defined as the time until the first successful connection to Tor. Non-finishing participants are assigned the maximum experiment time of 40:08.  Our changes to the interface did not have a significant impact in reducing the time participants took to successfully connect to Tor. The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). 
Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
%(Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$)
